\documentclass[]{article}

\usepackage[utf8]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{natbib} 
\usepackage{color}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{hyperref}

\usepackage{indentfirst} % indent first paragraph of section
%opening

\newcommand\todo[1]{\textcolor{red}{#1}}
\newcommand\done[1]{\textcolor{red}{#1}}
\newcommand\marie[1]{\textcolor{orange}{#1}}
\newcommand\bert[1]{\textcolor{red}{#1}}
\newcommand\julien[1]{\textcolor{green}{#1}}
\newcommand\alberto[1]{\textcolor{cyan}{#1}}
\newcommand\reply[1]{\textcolor{orange}{#1}}

\title{Clustering over user features and latent behavioral functions with dual-view mixture models \\ \texttt{-Reviews-}}

\author{}

\begin{document}
	\date{}
	\maketitle
	
	Dear Editors,
	
	We thank you again for this final comments. We addressed all these in our final manuscript. We provide short answers below.
	
	\bigskip
	\noindent
	\textbf{List of detailed responses:}\\
	(Q: editor comments.
	A: authors replies.)
	\subsection*{Editor-in-Chief}
	
	\vspace{3mm}	
	 \textbf{Q1}: While my previous comments have been addressed, I noticed one more problem with a reference:

\textit{
Plummer M, Best N, Cowles K, Vines K (2006) Coda: Convergence diagnosis and output analysis for mcmc. RNews 6(1):7-11, R package version 0.18-1}

These are actually 2 references (also note the proper capitalization of names):

\textit{Plummer M, Best N, Cowles K, Vines K (2006) 
CODA: Convergence diagnosis and output analysis for MCMC. R News 6(1):7-11.}

and the current "coda" package from 2015, accessible at
 
\url{https://cran.rproject.org/web/packages/coda/index.html}

Both should be cited in the main text and reference list.
Unfortunately, the "citation" information in R does not always
get updated - so it is usually a good idea to check the
information that is listed on the CRAN web site for a package.
		
\textcolor{blue}{\textbf{A1}: We have added both references.}
	
	\subsection*{Associate Editor}
	I would like to thank the authors for making this further revision. I agree that the modified title would be more suitable.
		\vspace{3mm}

	\textbf{Q1}: Regarding the example with the iris dataset I would suggest to clarify if the variable Species was used as true cluster labels. 
	
\textcolor{blue}{\textbf{A1}: We have specified that Species is use as the label for our points}

\vspace{3mm}

	\textbf{Q2}: One could try to remove all footnotes and also use different point characters in Figures 3, 6 and 8.
	
\textcolor{blue}{\textbf{A2}: All footnotes have been removed and plot lines have now different point shapes as well}.

\vspace{3mm}

	\textbf{Q3}: A reference to R is still missing, see citation() in R.
	
\textcolor{blue}
{\textbf{A3}: We have added the standard reference to R.}

	

	
\end{document}

